Regular singular Volterra equations on complex domains

### 2024-04-19 sima/correspondence/sima-v2-changes.tex
Remove contractions

\color{violet}
We addressed the co
\begin{itemize}
    \item We corrected the sign error that reviewer~2 noticed on line~275.
    \item We corrected the factorial $j!$ as reviewer~2 suggested on line~706.
     \item We corrected the factorial $j!$ as reviewer~2 suggested on line~730. We rewrote the decomposition of $Q$. 
     \item We corrected the sign error that reviewer~2 noticed on line~767.
      \item We corrected the typo that reviewer~2 noticed on line~781.
\end{itemize}
\color{black}
\closing{Best regards,}
\end{letter}
\end{document}

>>>>

\color{violet}
Reviewer~2:
\begin{itemize}
    \item We corrected the sign error that reviewer~2 noticed on line~275.
    \item We corrected the factorial $j!$ as reviewer~2 suggested on line~706.
     \item We corrected the factorial $j!$ as reviewer~2 suggested on line~730. We rewrote the decomposition of $Q$. 
     \item We corrected the sign error that reviewer~2 noticed on line~767.
      \item We corrected the typo that reviewer~2 noticed on line~781.
\end{itemize}
Reviewer~1:
\begin{itemize}
\item There is no universal convention for naming the coordinates on the spaces involved in the Laplace transform. Conventions we have seen include:
\begin{center}
\begin{tabular}{c|c|l}
Frequency varaible & Position variable & Source \\ \hline
$z$ & $\zeta$ & Mitschi \& Sauzin \\
$s$ & $t$ & Schiff \\
$\hbar$ & $s$ & Mari\~{n}o \\
\end{tabular}
\end{center}
From a physical perspective, the Laplace transform turns functions of position or time into functions of spatial or temporal frequency. The terms ``frequency'' and ``position'' thus unambiguously distinguish the two spaces involved in the Laplace transform. We use these terms to remind the reader which variable-naming convention we are using.
\end{itemize}
\color{black}
\closing{Best regards,}
\end{letter}
\end{document}
